Extending the WebID Protocol with Access Delegation

### 2012-07-19 paper.tex
remove comment package, fix bibstyle
add notes

\documentclass[a4paper]{llncs}
\usepackage{comment}
\usepackage{printlen} % Print lengths using specified units. 
%\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[utf8]{inputenc} % Umlaute üöä auch normal benutzen und nicht maskieren
\usepackage{color}
% http://www.ctan.org/tex-archive/fonts/ps-type1/cm-super/
\usepackage[T1]{fontenc} % use high quality fonts, please install cm-super
\usepackage[pdftex]{graphicx}
\graphicspath{{./Depictions/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.jpg,.png}
\usepackage[T1]{url}
\usepackage{listings}
\usepackage{subfig}
\usepackage{printlen} % Print lengths using specified units.
\usepackage{booktabs}
%\usepackage[textsize=tiny]{todonotes}
\usepackage{todonotes}

@@

All these applications have in common that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
In a WebID-enabled communication scenario, these devices use their own certificates for communication since we do not want to copy the browser certificate to these devices and we also do not want to save the passphrase on theses devices and services.

@@

\subsection{OAuth}
\todo{Andrei Sambra: Compare to oAuth}

@@

\bibliographystyle{IEEEtran}
\bibliography{webid}

>>>>

\documentclass[a4paper]{llncs}
\usepackage{printlen} % Print lengths using specified units. 
%\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[utf8]{inputenc} % Umlaute üöä auch normal benutzen und nicht maskieren
\usepackage{color}
% http://www.ctan.org/tex-archive/fonts/ps-type1/cm-super/
\usepackage[T1]{fontenc} % use high quality fonts, please install cm-super
\usepackage[pdftex]{graphicx}
\graphicspath{{./Depictions/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.jpg,.png}
\usepackage[T1]{url}
\usepackage{listings}
\usepackage{subfig}
\usepackage{printlen} % Print lengths using specified units.
\usepackage{booktabs}
%\usepackage[textsize=tiny]{todonotes}
\usepackage{todonotes}

@@

All these applications have in common that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.

We distinguish two different classes of applications here.
(1) Applications which provide their service to one user only and run on a device which can be accessed by one user only (e.g. a smartphone).
These applications have more in common with the users browser and can be seen as an extension to the user itself (\cite[extendedmind]).

In a WebID-enabled communication scenario, these devices use their own certificates for communication since we do not want to copy the browser certificate to these devices and we also do not want to save the passphrase on theses devices and services.

@@

\subsection{OAuth}
\todo{Andrei Sambra: Compare to oAuth}
\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}

@@

\bibliographystyle{plain}
\bibliography{webid}
